%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume
\documentclass[a4paper,margin,line]{resume}
\usepackage{url}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Subhash Kumar}
\begin{resume}

%__________________________________________________________________________________________________________________
	% Contact Information
	\section{\mysidestyle Contact\\Information}

	E-2206, Mantri Celestia \hfill +91 981 647 9040\\%
	Near Wipro Circle, Hyderabad\hfill agarwal1994@live.in\\%
	Telangana, India\hfill %

%__________________________________________________________________________________________________________________
	% Interests
	%\section{\mysidestyle Interests}

	%Programming, Software Development\\Machine Learning and its Applications%

%__________________________________________________________________________________________________________________
	% Education
	\section{\mysidestyle Education}

	\textbf{Indian Institute of Technology Mandi}, India\\%
	\textsl{B.Tech in Computer Science and Engineering with Minor in Management}\hfill August 2012 -- June 2016\vspace{-3mm}\\%
	\begin{list2}%
		\item Cumulative Grade Point Average: \textbf{6.98}%
	\end{list2}

	\textbf{Gaya College}, Gaya (Bihar), India\\%
	\textsl{Senior Secondary(B.S.E.B.)}\hfill 2011\vspace{-3mm}\\%
	\begin{list2}%
		\item Cumulative Average: \textbf{66.4\%}%

	\end{list2}%

	\textbf{Janta High School Dumariya}, Gaya (Bihar), India\\%
	\textsl{Secondary(B.S.E.B.)}\hfill 2010\vspace{-3mm}\\%
	\begin{list2}%
		\item Cumulative Average: \textbf{71\%}%

	\end{list2}%
%__________________________________________________________________________________________________________________
	\section{\mysidestyle Experiences}
	\textbf{Operating System Management and application development for t-hub}\vspace{0.5mm}\\%
	\textsl{\textbf{Smartron}}\hfill(July, 2016 -- present)\vspace{1mm}\\%
	t-hub is upcoming product by \textbf{Smartron} for iot product management. It will act as a central process unit for all iot product by Smartron. My role is to design and develop OS functionality and core Application for this. This include 
	\begin{list2}
		\item Process Management for t-hub.
		\item Design and Develop Core application such as Dashboard, Setting.
		\item Design security system to access t-hub and control application behavior.  
	\end{list2}

%__________________________________________________________________________________________________________________

	\section{\mysidestyle Undergraduate\\Thesis}
	\textbf{Network Management in Software Defined Network}\vspace{0.5mm}\\%	
	\textsl{Supervisor: Prof. Timothy A. Gonsalves, Director, IIT Mandi}\hfill(August, 2015 -- June 2016)\vspace{1mm}\\%	
	QoS Service and traffic Engineering in Home/Enterprise Network using Open-flow and SDN Concept and  reliability in that System.\\  Used Open-flow,  Mininet,  Pox  (Python based Controller),  Traffic  Classification  technique  and  QoS Policy.	
	\begin{list2}
	\item The major problem in the project to be tackled is to provide QoS and \textbf{service priority} on per user choice.
	\item \textbf{Different preference} option for different service for user.
	\item Easily deployable and controller running on cloud machine.
	\item Used SQL and Json for data parsing.
	\end{list2}
%________________________________________________________________________________________________________________
% Internships And Projectsjectee
	\section{\mysidestyle Internships And\\Projects}

	\textbf{Home Monitoring System}\vspace{0.5mm}\\
	\textsl{Smartron}\hfill(June, 2015 -- Aug, 2015)\vspace{1mm}\\
	Developed a cheap and Reliable System to Monitor Home using different parameter like Temperature,Humidity, Live video etc.  It generate warning based on processed data.\\
	Using rpi to behave as a central machine for server and controller and Python, to feed data generated by  Sensor  and  Bootstrap,  PHP,  HTML  to  analyze  data  and  Present  them  using  a website and show Notification Warning based on analyzed data.

	\section{\mysidestyle Course\\Projects}
	\textbf{Globalone}\hfill \textsl{Information And Database Systems}\vspace{1.0mm}\\%
	Built an \textbf{interactive organized photo base}, which had features like upload images, \textbf{buy/sell images}, \textbf{tag based auto complete search}, like or dislike, \textbf{paginated feeds}. Developed this app using Django web-framework, MySQL, HTML5, BootStrap CSS, AJAX.\\ Won the \textbf{first prize} out of \textbf{15 teams}, for this project.\\%

	\textbf{Network traffic analyser}\hfill \textsl{System Practicum}\vspace{1.0mm}\\%
	\textbf{CLI} Tool to Monitor \textbf{Network traffic} and generate Graph.\\
	Used \textbf{bash, SNMP, nmap, Python, gplot.}\\%

\pagebreak

	\textbf{Anti-collision System for blind turns}\hfill \textsl{Design Practicum}\vspace{1.0mm}\\%
	Develop a Product to detect vehicles on both side of blind curve and prevent accident, Specially in Fog area.\\
	This will give warning through light, sound or both based on weather condition.\\
	Used\textbf{ C, Arduino} for this project.%
	
	\textbf{Hotel/Canteen Ordering System}\hfill \textsl{Database Practicum}\vspace{1.0mm}\\
	Hotel Management System which has feature like Order food, book Table/Room, give rating to service, promotional offer and a Admin interface.\\
	Used\textbf{ PHP, MySQL, HTML, CSS}.%

%__________________________________________________________________________________________________________________
	% Honours and Awards
	\section{\mysidestyle Technical\\Skills}
	\textbf{Languages}: C, C++, Python, PHP\\%
	\textbf{Web Development}: HTML, CSS, JavaScript, Bootstrap\\%
 	\textbf{Database Management}: MySQL\\%
 	\textbf{Operating System}: Windows, Linux(Ubuntu), Mac, Snappy (Ubuntu-core). \\%
 	\textbf{Misc.}:  \LaTeX\ , Django web-framework, R, SNMP tools, Adobe Photoshop, node.js \\%

	%__________________________________________________________________________________________________________________
	% Scholastic Achievements

	%________________________________________________________________________________________________________________
    % Competitive Programming



%______________________________________________________________________________________________________________________
	\section{\mysidestyle Position Of\\Responsibility}

	\textbf{Coordinator, Space Technology and Astronomy Cell, IIT Mandi}\hfill(May, 2014 -- June, 2015)\vspace{0.5mm}\\%
	Served  as  the  coordinator  of  Astronomy  Club,  IIT  Mandi.   The  club  is  responsible  for  organizing many events such as \textbf{Star gazing}, workshops, etc.  We have also started research section in field of Astronomy.\\
	\textbf{Web Coordinator , Exodia (Cult-Tech Fest), IIT MANDI}\hfill(2015)\vspace{0.5mm}\\%
	%\textbf{Treasurer/Secretary, ACM Student Chapter, IIT Mandi}\hfill(Nov, 2013 -- May, 2014)\vspace{0.5mm}\\%
	The Main responsibility as a web coordinator of Exodia'15 as to built a website for Fest and manage Server, Data and Application to promote Fest all over the India.\\%
	\textbf{Coordinator, National Service Scheme, IIT MANDI}\hfill(Sep 2012 May -- 2014)\vspace{0.5mm}\\%
	Served as the Coordinator of NSS, IIT Mandi which was preceded by the role of co-coordinator from Sept, 2012 to Sept, 2014.  Organized many events as blood donation camp, teaching students at orphanages, tree plantation program, etc. Also made Website for NSS and started Design and Publicity Section to increase creativity.\\%

	\section{\mysidestyle Relevant\\Coursework}
	\textbf{Computer Science:} Data Structures, Computation For Engineers, Computer Organization, Paradigms of Programming, Analysis And Design of Algorithms, Software Engineering, Network Management System, Information And Database Systems, Communicating Distributed Processes, Data Mining For Decision Making, Big Data and Map Reduce. \vspace{0.5mm}\\%
	\textbf{Management Courses:} Economics, Organization Management, Managerial Decision Making, Financial Accounting, Financial Management.
%______________________________________________________________________________________________________________________
\section{\mysidestyle Extra\\Curriculars}

\begin{list2}
	\item Represented IIT Mandi in the \textbf{Inter-IIT Sport Meet} as \textbf{Hockey Player} in 2012, 2013.
	\item 	Social Service: Taught children of rural areas in an initiative by \textbf{Prayas}, IIT Mandi
	\item Represented IIT Mandi in the \textbf{Inter-IIT Tech-meet} IIT Bombay , 2014 and IIT Khadagpur, 2015 in \textbf{Messier Marathon}.
	\end{list2}

\section{\mysidestyle References}

	\textbf{Prof.  Timothy A. Gonsalves}\\
	Director, IIT Mandi\\
	Email :  tag@iitmandi.ac.in


%	\textbf{Gaurav Agarwal}\vspace{0.5mm}\\%
%	Chief Technology Officer, healthkart.com\\
%	Email : gaurava@gmail.com


\end{resume}
\end{document}
%______________________________________________________________________________________________________________________
% EOF
